%%
%% Copyright (c) 2018-2019 Weitian LI <wt@liwt.net>
%% CC BY 4.0 License
%%
%% Résumé
%% ------
%% A short document (1-2 pages) to sum up the job-related accomplishments
%% and experience.
%%
%% Checklist
%% ---------
%% * Contact Information
%% * Work History / Experience
%% * Education
%% * Skills
%% * Summary & Objective (optional)
%% * Hobbies & Interests (optional)
%%
%% Credits
%% -------
%% * CV vs. Resume: What is the Difference? When to Use Which?
%%   https://uptowork.com/blog/cv-vs-resume-difference
%% * How to Make a Resume: A Step-by-Step Guide (+30 Examples)
%%   https://uptowork.com/blog/how-to-make-a-resume
%% * Entry-Level Resume: Sample and Complete Guide (+20 Examples)
%%   https://uptowork.com/blog/entry-level-resume-example
%%
%% Created: 2018-04-14
%%

% English version
\documentclass{resume}

% Adjust icon size (default: same size as the text)
\iconsize{\Large}

% File information shown at the footer of the last page
\fileinfo{%
  \faCopyright{} 2023, Yipeng Liu \hspace{0.5em}
  \creativecommons{by}{4.0} \hspace{0.5em}
  \githublink{lwpie}{resume} \hspace{0.5em}
  \faEdit{} \today
}

\name{Yipeng}{Liu}

\keywords{Linux, Python, C, Shell, DevOps, SysAdmin}

% \tagline{\icon{\faBinoculars}} <position-to-look-for>}
% \tagline{<current-position>}

% \photo{<height>}{<filename>}

\profile{
  \mobile{15::24652}
  \email{liu@yipe.ng}
  \github{lwpie} \\
  % \degree{Ph.D.}
  \university{IIIS, Tsinghua University}
  \birthday{April 2002}
  \home{Shanghai}
  % Custom information:
  % \icontext{<icon>}{<text>}
  % \iconlink{<icon>}{<link>}{<text>}
}

\begin{document}
\makeheader

%======================================================================
% Summary & Objectives
%======================================================================
\vspace{0.5em}
Highly motivated Ph.D. student of IIIS, Tsinghua University with robust skills in design and programming.
Proficient in coding while enthusiastic about computer technologies.
Open-source advocator, proudly a member of the \link{https://tuna.moe}{\texttt{TUNA}} community.
Have participated in numerous projects and competitions across both software and hardware domains, winning several top awards.
Cycling and swimming lover, having a strong sense of team spirit and communication.

%======================================================================
\sectionTitle{Competences \& Languages}{\faWrench}
%======================================================================
\begin{competences}[10em]
  \separator{0.1em}

  \comptence{Programming}{%
    \texttt{C/C++,Python,Rust}
  }
  \comptence{}{%
    \texttt{SQL,Shell,Web}
  }

  \comptence{\icon{\faLanguage} English}{%
    Shanghai NMET 137
  }
  \comptence{}{%
    CET4 647 / CET6 623
  }
\end{competences}

%======================================================================
\sectionTitle{Research Experiences}{\faGraduationCap}
%======================================================================
\begin{educations}
  \separator{0.2em}

  \education%
    {2021.06}%
    [Present]%
    {Institute for Interdisciplinary Information Sciences}%
    {Huanchen Zhang}%
    {Database}%
    {Automatic reclustering algorithm for cloud data warehouse}
  
  \separator{0.5ex}
  \education%
    {2020.02}%
    [2020.10]%
    {Department of Computer Science and Technology}%
    {Zhiyuan Liu}%
    {NLP}%
    {Network structure on rumor propagation during the COVID-19 epidemic}
\end{educations}

%======================================================================
\sectionTitle{Projects \& Awards}{\faBriefcase}
%======================================================================
\begin{awards}
  \separator{0.2em}

  \award%
    {2022.06}%
    {Outstanding Graduate}%
    {Department of Computer Science and Technology.}
  \separator{0.5em}

  \study%
    {2021.08}%
    [2021.04]%
    {CSC Compiler Contest}%
    {C++,ARM}%
    {First Prize, Bisheng Special Award.}
  \separator{0.5em}

  \study%
    {2021.05}%
    [2020.10]%
    {NaiveDB}%
    {C++,SQL}%
    {On-disk database system with support of INDEX, JOIN, MVCC and WAL.}
  \separator{0.5em}

  \award%
    {2020.10}%
    {Scholarships}%
    {Academic Progress, Social Work, Innovation, Volunteer.}
  \separator{0.5em}

  \study%
    {2021.01}%
    [2020.09]%
    {Untitled Router}%
    {Verilog,RISC-V,C}%
    {\texttt{RIPv2} compatible router on self-designed \texttt{RISC-V} processor of five-stage pipelining.}
  \separator{0.5em}

  \study%
    {2020.04}%
    [2020.03]%
    {109\textsuperscript{th} Anniversary of Tsinghua University Online}%
    {Flask,Vue}%
    {Over a million visits with several letters of thanks from senior alumni.}
  \separator{0.5em}

  \study%
    {2019.12}%
    [2019.10]%
    {Electronic Design Competition}%
    {STM32,C}%
    {First Prize, SenseTime Special Award.}
  \separator{0.5em}

  \award%
    {2019.04}%
    {Tsinghua's Challenge Cup}%
    {Second Prize, one patent.}
  \separator{0.5em}

  \award%
    {2017.05}%
    {International Mathematical Modeling Challenge}%
    {Outstanding Winner.}
  \separator{0.5em}

  \award%
    {2016.04}%
    {Mathematical Contest in Modeling}%
    {Meritorious Winner.}

\end{awards}

\end{document}
